Carbonate chemistry at Ny-Ålesund

### 2021-06-09 awipev-CO2.Rmd
fiddling with stratification plot

@@

@@

p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = density)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = c("0-4", "8-12")) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
```

>>>>

sal_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=sal_delta)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous("Salinity", limits = c(-1.1, 0.8), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

temp_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=temp_delta)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous("Temperature", limits = c(-3, 3), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

@@

p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = density)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
  scale_x_discrete(labels = c("0-4", "8-12")) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

den_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=den_delta)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous("Density", limits = c(-1.5, 0.5), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# we look at pHint_tot_sf 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::mutate(depth_group = depth_group_pressure) %>% 
  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
  dplyr::filter(depth == 2 | depth == 10) %>% 
  group_by(depth, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))

tmp_delta <- tmp %>% 
  group_by(depth, montht) %>% 
  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>% 
  tidyr::pivot_wider(names_from = depth, values_from = pH_tot_sf_med) %>% 
  dplyr::rename(median0_4m = "2",
                median8_12m = "10") %>% 
  dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
kable(tmp_delta, digits = 3, caption = "Median seafet pH with (median0_4m - median8_12m)")

p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pH vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

pH_delta_plt <- tmp_delta %>% 
  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
  scale_x_discrete("Month", expand = c(0, 0)) +
  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.2, 0.1), expand = c(0, 0)) +
  geom_col(fill="blue") +
  geom_hline(yintercept = 0) +
  annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
  annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
  Mytheme(size_labs = 12) +
  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
deltas <- deltas + plot_annotation(tag_levels = 'a')
ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
```
